\documentclass[dvips,xcolor=pst]{beamer}
%\documentclass[dvips,handout,xcolor=pst]{beamer}
%\documentclass[letterpaper]{article}
%\usepackage{beamerarticle}
%\newcommand{\newblock}{} % a hack for bibtex.
\usepackage{pstricks}
%\usepackage{hyperref}
%\usepackage[authoryear]{natbib}
\usepackage{graphicx}
\usepackage{multimedia}
\usepackage{pgfpages}
\usepackage{arydshln}
\usepackage{commath}
\usepackage{vector}
%\usepackage{cancel}
\usepackage{ulem}
\usepackage{listings}
%\usepackage{times}

\graphicspath{{pysci_eps/}}

\newcommand{\defeq}{\ensuremath{\buildrel {\text{def}}\over{=}}} 

%\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{Luebeck}
%\usetheme{Pittsburgh}
%\usetheme{CambridgeUS}
\usetheme{default}
%\usecolortheme{seagull}
%\setbeameroption{show notes}
%\setbeameroption{show only notes}
%\pgfpagesuselayout{2 on 1}[letterpaper,border shrink=0.2in]
%\usefonttheme[stillsansseriftext]{serif}
\usefonttheme[onlymath]{serif}

\title{September Meeting}
%
\institute{Python Hsinchu User Group}
%
\date[2011/9/19]{September 19, 2011}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}{
%
Schedule
%
}
\begin{itemize} \large
  \item 7:30pm -- 7:40pm Welcome
  \item 7:40pm -- 7:50pm Introduction of the Group
  \item 7:50pm -- 8:00pm Introduction of the Members
  \item 8:00pm -- 8:20pm Talk: ``Introduction to NumPy, SciPy, and Matplotlib''
  \item 8:00pm -- 8:30pm Questions and Answers
  \item 8:30pm -- 9:00pm Open Discussion on ``What Do You Expect for PyHUG''
  \item 9:00pm See You Next Time
\end{itemize}
\end{frame}

\begin{frame}{
%
Python Hsinchu User Group
%
}
\begin{itemize} \large
  \item Objectives:
  \begin{itemize} \large
    \item Organize regular meetings to connect Python programmers.
    \item Encourage Python programmers to discuss their problems and improve
    their skills.
    \item Promote Python in the engineering and scientific practices.
  \end{itemize}
  \item The program of PyHUG monthly meetings:
  \begin{itemize} \large
    \item A Monday night of every month.
    \item Allocate two short talks.
    \item Open discussions and hacking.
  \end{itemize}
  \item Current format of the short talks:
  \begin{itemize} \large
    \item 20 minutes for each talk and 10 minutes for questions.  Total is 30
    minutes.
    \item No constraints on the topics.
  \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{
%
Online Resources
%
}
\begin{itemize} \large
  \item Meetup page: \url{http://www.meetup.com/pythonhug/}
  \item python.tw mailing list (Google group):
  \url{https://groups.google.com/forum/\#!forum/pythontw}
  \item IRC room is at Freenode/\#python.tw:
  \url{http://webchat.freenode.net/?channels=python.tw}
  \item This slide: {\tiny
  \url{https://bitbucket.org/yungyuc/talk/raw/tip/20110919_pysci/archive/pysci_welcome.pdf}}
\end{itemize}
\end{frame}

\begin{frame}{
%
Introduce Yourself
%
}
\begin{itemize} \large
  \item Name (and nick name if you have)
  \item How long have you used Python
  \item Your coding interests (web, mobile, signal processing, etc.)
  \item Other things you want to share
\end{itemize}
\end{frame}

\begin{frame}{
%
%
}
\begin{center} \Huge
  Seminar Session (20 Minutes) \\
  (10 Minutes for Questions)
\end{center}
\end{frame}

\begin{frame}{
%
%
}
\begin{center} \Huge
  5 Minutes Left
\end{center}
\end{frame}

\begin{frame}{
%
%
}
\begin{center} \Huge
  \alert{1 Minute Left}
\end{center}
\end{frame}

\begin{frame}{
%
Future Planning
%
}
\begin{itemize} \large
  \item Monthly meetings.
  \begin{itemize} \large
    \item Locations.
    \item Subjects.
    \item Time and format.
  \end{itemize}
  \item Other meetings.
  \begin{itemize} \large
    \item Sprints or hackathons.
    \item Special topics.
  \end{itemize}
  \item Other wild ideas.
\end{itemize}
\end{frame}

\end{document}

% vim: set spell:
