\documentclass[dvips,xcolor=pst,14pt]{beamer}
%\documentclass[dvips,handout,xcolor=pst]{beamer}
%\documentclass[letterpaper]{article}
%\usepackage{beamerarticle}
\newcommand{\newblock}{}
\usepackage{pstricks}
%\usepackage{hyperref}
%\usepackage[authoryear]{natbib}
\usepackage{graphicx}
\usepackage{multimedia}
\usepackage{pgfpages}
\usepackage{arydshln}
\usepackage{commath}
\usepackage{vector}
%\usepackage{cancel}
\usepackage{ulem}
\usepackage{listings}
\usepackage{fancyvrb}
%\usepackage{times}

\graphicspath{{solvcon_eps/}}

\newcommand{\defeq}{\ensuremath{\buildrel {\text{def}}\over{=}}} 

%\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{Luebeck}
%\usetheme{Pittsburgh}
\usetheme{CambridgeUS}
%\usecolortheme{seagull}
%\setbeameroption{show notes}
%\setbeameroption{show only notes}
%\pgfpagesuselayout{2 on 1}[letterpaper,border shrink=0.2in]
%\usefonttheme[stillsansseriftext]{serif}
\usefonttheme[onlymath]{serif}

\title[Python Taiwan]{Python Taiwan}
%
\author[\href{http://www.python.org.tw/}{PyTWer}]%
{\href{http://www.python.org.tw/}{From Python Taiwan Guys}}
%
\institute[\href{http://www.python.org.tw/}{PyTW}]%
{\href{http://www.python.org.tw/}{Python Taiwan}}
%
\date[2012/9/15]{PyCon Japan 2012 \\ September 15}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}{
%
Hello Friends
%
}
\begin{itemize}
  \item Thank you for all the hard works behind this great event.
  \item I am Yung-Yu Chen from \alert{Taiwan}: \url{yyc@solvcon.net}.
  \begin{itemize}
    \item A.k.a. yungyuc/yyc.
  \end{itemize}
  \item I write Python everyday.
\end{itemize}
\end{frame}

\begin{frame}{
%
Python Taiwan
%
}
\begin{itemize}
  \item User groups:
  \begin{itemize}
    \item \alert{PyHUG} (Python Hsinchu User Group):
    \url{http://www.meetup.com/pythonhug/}
    \item \alert{Taipei.py}: \url{http://taipei.python.org.tw/}
  \end{itemize}
  \item We are working on a portal site: \url{http://www.python.org.tw/}
\end{itemize}
\end{frame}

\begin{frame}{
%
PyCon Taiwan
%
}
\begin{itemize}
  \item In June 2012 we had the first PyCon Taiwan!
  \begin{itemize}
    \item 260 people attended.
    \item Thank you guys from Japan supporting us in person!
  \end{itemize}
  \item Next year it will be in May 2013.
  \begin{itemize}
    \item We'll make it more international-oriented.
    \item Pythonistas of 300, 400, 500, or more?
    \item Come to share your Python pride.
    \item \url{http://tw.pycon.org/}
  \end{itemize}
\end{itemize}
\end{frame}

\end{document}

% vim: set spell:
